---
title: "Lab 01"
author: "Nilanjana Dey"
date: "2023-11-20"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
a=3
```

#Introduction
```{r}
a=c(5,6) #basic operations
a
```

#TO FIND THE SAMPLING ERROR AND THE SAMPLING DISTRIBUTION
```{r}
#DATASET-The data give the speed of cars and the distances taken to stop.The data has been recorded in the 1920s.
c=cars
c
```


```{r}
library(help="datasets")#get the description of all the in-built datasets
```


```{r}

dim(cars)#rows and columns in the dataset
```

```{r}
head(cars)
tail(cars)
```
```{r}
summary(cars)#descriptive statistics
```
#The variable speed of cars varies from 4 km/hr to 25 km/hr

##HISTOGRAM
```{r}
hist(cars$speed,xlab="Speed",ylab="frequency",main=" Histogram of Speed ",col=blues9)
```
```{r}
sd(cars$speed) #standard error of the speed

```
sd value is higher than 0 which indicates that the data points are not close to mean.


## Population
```{r}
population=cars$speed
population
```
```{r}
#choosing 20 observations in the sample
samplesize=20
#choosing 20 samples from the population using simple random sampling without replacement

s1=sample(population,samplesize,replace=FALSE)
s1
```
```{r}
# Finding mean of the sample
mean(s1)
```
##STANDARD ERROR
```{r}
#STANDARD ERROR
sd(s1)/sqrt(samplesize)
```


```{r}

samplesize1=10
s2=sample(population,samplesize1,replace=FALSE)
s2
mean(s2)
```
```{r}
#standard error
sd(s2)/sqrt(samplesize1)
```
##SAMPLING DISTRIBUTION
```{r}
hist(s1)
```
```{r}
hist(s2)
```
#replicate():used to evaluate an expression N number of times repeatedly.
#Here, it is replicated 1000 times

```{r}
samp_dist=replicate(1000,mean(sample(cars$speed,20,replace=FALSE)))
samp_dist
```
```{r}
head(samp_dist)
mean(samp_dist)
```
```{r}
var(samp_dist)
```
```{r}
hist(samp_dist)
```








