---
title: "Lab-06"
author: "Nilanjana Dey"
date: "2024-01-03"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# INTRODUCTION :

The following dataset comprises the various smartphones trending in the market and their respective features. The dataset has been taken from Kaggle.

The following columns are as follows:

 brand_name 
 model               
 price            
 rating  
 has_5g         
 has_nfc        
 has_ir_blaster  
 processor_brand
 num_cores     
 processor_speed 
 battery_capacity 
 fast_charging_available
 fast_charging     
 ram_capacity   
 internal_memory  
 screen_size
 refresh_rate    
 num_rear_cameras 
 num_front_cameras      
 os : operating system
 primary_camera_rear 
 primary_camera_front 
 extended_memory_available
 extended_upto    
 resolution_width 
 resolution_height

```{r}
# The dataset is imported.

library(readxl)
smartphones <- read_excel("C:/Users/NILANJANA/Downloads/smartphones_cleaned_v6.xlsx")
View(smartphones)
```
```{r}
# There are 980 observations 
dim(smartphones)
```
```{r}
# the first 6 observations are displayed
head(smartphones) 
```
```{r}
# the last 6 observations are printed.
tail(smartphones)
```

```{r}
# HERE ARE DEALING WITH THE DESCRIPTIVE ANALYSIS OF THE ENTIRE DATASET.

summary(smartphones)
```
## VISUALIZATION OF SOME OF THE CATEGORICAL COLUMNS OF THE DATASET

```{r}
# HERE WE ARE REPRESENTING "extended_memory_available" USING FREQUENCY PLOT

x = table(smartphones$extended_memory_available)
barplot(x,xlab = "YES=1 : NO=0",ylab="COUNT",main="AVAILABLITY OF EXTENDED MEMORY",col = "pink")

# THE PLOT BELOW SHOWS THAT THE NO. OF SMARTPHONES MADE HAVE THE FEATURE OF "EXTENDED MEMORY"
```
```{r}
# Here we shall visualize the smartphones having different ratings using pie chart

library(ggplot2)
library(dplyr)

k=as.character(smartphones$rating)

ggplot(smartphones, aes(x = "", fill = k)) +
  geom_bar(position = "fill", width = 1,color="black") +coord_polar(theta = "y")+guides(fill = guide_legend(title = "Rating of the Smartphones"))+theme(axis.title.y = element_blank())+labs(title="PIE CHART FOR SMARTPHONES WITH DIFFERENT RATINGS")

# From the plot given below we can conclude that the count of different ratings is more or less same
 
```
```{r}

# Here we are plotting the no. of smartphones having 5g and not having 5g.

library(ggplot2)


ggplot(smartphones, aes(x = smartphones$has_5g, fill = smartphones$has_5g)) +
  geom_bar(show.legend=FALSE) +
  labs(title = "Bar Plot of Smartphones having 5g",x="Has 5g or not", y = "Count")

# From the plot given below the no. of smartphones having 5g is more
```
```{r}
# Here we are plotting the frequency plot of different processor brands

library(ggplot2)

ggplot(smartphones, aes(x = smartphones$processor_brand, fill = smartphones$processor_brand)) +
  geom_bar(alpha=0.8,show.legend =FALSE ) + coord_flip()+
  labs(title = "BAR PLOT FOR PROCESSOR BRANDS", y = "COUNT", x = "BRAND NAME")

# The plot given below shows that 'snapdragon' is mostly used followed by 'helio' and 'dimesity'
```
```{r}

# Here we are plotting the no. of smartphones having the fast charging facility or not
library(ggplot2)

m=as.character(smartphones$fast_charging_available)
ggplot(smartphones, aes(x =m , fill = m)) +
  geom_bar(show.legend=FALSE) +
  labs(title = "FREQUENCY PLOT FOR AVAILABLITY OF FAST CHARGING FACILITY", x = "Rating", y = "Count")

# The following plotted graph shows that fast charging facility is available in most of the mobiles

```
```{r}
# Here we are representing the different kinds of ram_capacity available in the smartphones using radial plot

library(ggplot2)

d=as.character(smartphones$ram_capacity)

ggplot(smartphones, aes(x = d, fill = d)) +
  geom_bar(show.legend=FALSE) + coord_polar()+
  labs(title = "Radial Plot for Ram_Capacity", x = "RAM CAPACITY", y = "Count",color="RAM CAPACITY")

# The following graph indicates that the most of the smartphones have ram_capacity = '8' followed by '6' and '4'
```
```{r}
# Here we are plotting the frequency plot for different types of os used in smartphones

library(ggplot2)


ggplot(smartphones, aes(x = smartphones$os, fill = smartphones$os)) +
  geom_bar() +
  labs(title = "Bar Plot for Smartphone OS ", x = "OS TYPE", y = "Count")

# From the plot given below we conclude that 'android' is the most widely used os.
```


```{r}
# Frequency plot for Availability of IR blaster
library(ggplot2)


ggplot(smartphones, aes(x = smartphones$has_ir_blaster, fill = smartphones$has_ir_blaster)) +
  geom_bar() +
  labs(title = "Frequency Plot for Availablity of IR BLASTER",y = "Count")

# The following plot indicates that the most of the smartphones have ir-blaster
```
# TEST FOR SINGLE POPULATION PROPORTION

# AIM : We shall consider one categorical column from the dataset and perform the single proportion test.

target variable = 'has_5g'

Objective : We shall test whether the proportion of smartphones having 5g facility is equal to the assumed value of 0.56.



```{r}
target_var=smartphones$has_5g 

```

```{r}
# a sample of 300 observations is taken with replacement
sample1=sample(target_var,300,replace=TRUE)
```

```{r}
# The sample taken , is converted into a dataframe
s=as.data.frame(sample1)
```
```{r}
# Now we get the contingency table showing the total no. of 'TRUE' and 'FALSE' values.
library(dplyr)
count(s,sample1)
```
##HYPOTHESIS TESTING

BOTH-TAILED TEST

H0: P0=O.56
VS
H1: P1!=0.56
```{r}

n=300
x=176
prop.test(x, n, p = 0.56, alternative = "two.sided",
          correct = TRUE)

# Interpretation : The p-value is >0.05. Therefore we accept the H0 which implies that the true proportion of smartphones having 5g facility is equal to the assumed value of 0.56.

```
QUESTION 8:

Given : Sample size=600 , no. of students favoring online teaching=180

AIM : We want to test whether the proportion of students favoring online education is equal to the assumed value of '30% students favoring online education'

##HYPOTHESIS TESTING

BOTH-TAILED TEST

H0: P0=O.3
VS
H1: P1!=0.3


```{r}
n=600
x=180
prop.test(x, n, p = 0.3, alternative = "two.sided",
          correct = TRUE)

# Interpretation : The p-value is 1 which is more than 0.05 which indicates the acceptance of H0, i.e, our assumption is correct.
```

