---
title: "Lab-10"
author: "Nilanjana Dey"
date: "2024-02-12"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
nike <- read_excel("C:/Users/NILANJANA/Downloads/nike_data_2022_09.xlsx")
View(nike)

```

```{r}
library(readxl)
netflix <- read_excel("C:/Users/NILANJANA/Downloads/Best Movie by Year Netflix.xlsx")
View(netflix)
netflix
```

```{r}
# the libraries are installed
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(broom)
library(AICcmodavg)
library(dplyr)
```

```{r}
# we try to identify the levels of "MAIN_GENRE" factor
netflix$MAIN_GENRE=as.factor(netflix$MAIN_GENRE)
levels(netflix$MAIN_GENRE)
```
```{r}
# we try to identify the levels of "MAIN_PRODUCTION" factor
netflix$MAIN_PRODUCTION=as.factor(netflix$MAIN_PRODUCTION)
levels(netflix$MAIN_PRODUCTION)
```
1) Movie data:
A)Test whether the genre and main production company of a movie is having any significant effect on the the IMDB score.

We will first check for difference with interaction effect between factors "MAIN_PRODUCTION" and "MAIN_GENRE".

H0A: There is no significant difference in the SCORE with 7 levels of 'MAIN_PRODUCTION' factor μ1=μ2=μ3=μ4=μ5=μ6=μ7

H0B: There is no significant difference in the SCORE with 12 levels of 'MAIN_GENRE' factor

H0AB: The interaction effect of "MAIN_PRODUCTION" and "MAIN_SCORE" is insignificant.

vs

H1A: atleast one inequality in H0A
H1B: atleast one inequality in H0B
H1AB: atleast one inequality in H0A

```{r}
two.way <- aov(SCORE ~ MAIN_PRODUCTION*MAIN_GENRE, data = netflix)
summary(two.way)

#Interpretation: We can see that the two factors and their interaction effect is insignificant which is evident from the p-value.In every case we accept the H0.
```
```{r}
#Without interaction effect
two.way <- aov(SCORE ~ MAIN_PRODUCTION+MAIN_GENRE, data = netflix)
summary(two.way)

#Interpretation: Here also the two factors are concluded to be insignificant as p-value>0.05. Hence we don't perform the Tukey-HSD test.
```


2) For the given nike data, test whether the average price of nike products that are in stock and out of stock are significantly differing or not.[ Note: Check the assumptions first]




```{r}
population_1=filter(nike,availability=='InStock')

```



```{r}
sample_1=sample(population_1$price,20,replace=FALSE)
sample_1

```
```{r}
population_2=filter(nike,availability=='OutOfStock')
population_2
```

```{r}
sample_2=sample(population_1$price,10,replace=FALSE)
sample_2
```
#Two-tailed 
H0:MEAN_1=MEAN_2 
VS H1:MEAN_1!=MEAN_2

```{r}
library(BSDA)
z.test(x=sample_1,y=sample_2,
alternative = "two.sided",
mu = 0,
sigma.x = sd(population_1$price),
sigma.y = sd(population_2$price),
conf.level = 0.95
)
```

4)Test whether the proportion of nike products that are in white, black, Navy are significantly different or not.




```{r}
# our target variable is color
target_var=nike$color
```

```{r}
# a sample of 50 observations are drawn
sample1=sample(target_var,50,replace=TRUE)
sample1
```
```{r}
# a dataframe is created from the samples
s=as.data.frame(sample1)
s
```
```{r}

count(s,sample1)
```
H0 : the proportion of nike products that are in white, black, Navy are same.

vs 

H1 : the proportion of nike products that are in white, black, Navy are significantly different.



```{r}


x=c(3,1,4)
n=c(50,50,50)
prop.test(x, n, alternative = "two.sided", conf.level = 0.95)

#Interpretation: The proportion of nike poducts in white,black and navy blue is sme which is indicated by the acceptance of H0 from the p-value.

```
3)Take a sample of 250 from the population and test whether the variance of price of nike products is 45. Validate using an appropriate test.

A sample of 25 observations are taken and replicated 250 times.Now we conduct the one-sample variance test where the test sample follows chi-square test.


```{r}
#replicating the sample 

samp_dist=replicate(250,mean(sample(nike$price,25,replace=TRUE)))

```
H0 : sigma.squared = 45 vs H1 : sigma.squared != 45
```{r}
library(EnvStats)
varTest(samp_dist, alternative = "two.sided", conf.level = 0.95, sigma.squared =45)

#Interpretation: We reject H0 which implies that the varinace is not 45.
```






