---
title: "LAB-09"
author: "Nilanjana Dey"
date: "2024-01-31"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# The Data set is loaded.
library(readr)
DRUG <- read_csv("C:/Users/NILANJANA/Downloads/Exercise2_data.csv")
View(DRUG)
DRUG
```

```{r}
# the libraries are installed
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(broom)
library(AICcmodavg)
```

```{r}
# we try to identify the levels of "Procedure" factor
DRUG$Procedure=as.factor(DRUG$Procedure)
levels(DRUG$Procedure)
```
```{r}
# we try to identify the levels of "Gender" factor
DRUG$Gender=as.factor(DRUG$Gender)
levels(DRUG$Gender)
```
```{r}
# we try to identify the levels of "Gender" factor
DRUG$Drug=as.factor(DRUG$Drug)
levels(DRUG$Drug)
```


ONE-WAY ANOVA:

H0:There is no significant difference in the PreOpScore with 2 levels of 'Drug' factor -> μ1 = μ2 

vs

H1:μ1 != μ2 

```{r}
# we perform the one-way anova test for factor 'Drug'
oneway <- aov(PreOpScore~Drug, data = DRUG)
summary(oneway)
```
##INTERPRETATION : The p-value is greater than 0.05 which indicates the acceptance of H0 which denotes that the 'Drug' factor is insignificant and does not have any effect on the "PreOpScore".



H0:There is no significant difference in the PreOpScore with 2 levels of 'Gender' factor -> μ1 = μ2 

vs

H1:μ1 != μ2 



```{r}
oneway2 <- aov(PreOpScore~Gender, data = DRUG)
summary(oneway2)

##INTERPRETATION : The p-value is less than 0.05 which indicates the rejection of H0 which denotes that the 'Drug' factor is significant and does effect the "PreOpScore".
```
## PAIRED COMPARISON TEST 


```{r}

TukeyHSD(oneway2, conf.level=.95)

#Interpretation : Both of levels affect the "PreOpScore" which is evident from the p-value being less than 0.05.
```
```{r}
## Graphical Representation of the confidence interval for the above test
plot(TukeyHSD(oneway, conf.level=.95), las = 2)
```
##TWO WAY ANOVA

We will first check for difference with interaction effect between factors "Gender" and "Procedure".

H0A: There is no significant difference in the PreOpScore with 2 levels of 'Gender' factor μ1 = μ2 

H0B: There is no significant difference in the PreOpScore with 2 levels of 'Procedure' factor μ1 = μ2 

H0AB: The interaction effect of "Gender" and "Procedure" is insignificant.

vs

H1A: atleast one inequality in H0A
H1B: atleast one inequality in H0B
H1AB: atleast one inequality in H0A



```{r}
two.way <- aov(PreOpScore ~ Gender*Procedure, data = DRUG)
summary(two.way)

##INTERPRETATION : We can conclude that the interaction effect is not significant here which is evident from the p-value.But 'Gender' factor is significant.
```
```{r}
## We again perform the two-way anova test without interaction effect.
two.way2 <- aov(PreOpScore ~ Gender+Procedure, data = DRUG)
summary(two.way2)

## Interpretation : "Gender" is the significant factor.
```
```{r}
## We perform the paired comparison test.
TukeyHSD(two.way2, conf.level=.95)
```
```{r}
## Graphical representation of the confidence intervals
plot(TukeyHSD(two.way2, conf.level=.95), las = 2)
```

